Solar jet observed at the limb in SDO/SST

### 2016-08-08 paper/ms_temp_paper.tex
finished doppler seciton

% will need to rewrite this at a later date
This particular feature, as has already been mentioned, has two events in which material is accelerated upwards into the solar atmosphere.
An examination of the dopplergrams reveals little in the way of rotational behaviour, however the second event demonstrates a characteristic division of red and blue.

@@

dop_frames = [76,77,78,79,80,81,82,83,84]
frame_numbers = np.arange(75,90)

>>>>

The result of applying the above method to the SST dataset is presented in \cref{fig:dop_grid}.
This particular feature, as has already been mentioned, has two events in which material is accelerated upwards into the solar atmosphere.
The first event is not readily visible in the dopplergrams, difficult as it is to pick out against a line of spicule-like features all showing redshifts, away from the viewewing direction.
This result is to be expected given the we have demonstrated movement away from the 'camera' in \cref{fig:stereo}.
Whereas, the second expulsion of material, originating at $07:37$, exhibits the classic behaviour of a rotating feature in dopplergrams, a red/blue split over the body of the feature.

In order to examine the behaviour of the jet we take a horizontal slit across the midpoint of the jet in order to study its evolution in detail.
It is clear that the second event comes from a similarly small element to the first and evolves upwards, joining the full formation of the jet, hence why the apparent rotation of the jet does not appear to spread across the rest of the jet as seen in H$\alpha$.

As the jet evolves we see an initial red shift

@@

dop_frames = [76,77,78,79,80,81,82,83,85]
frame_numbers = np.arange(75,90)
